---
Assignment: Reproducible Research Project Assignment 2

File name: "PA2_template.Rmd"
Autor: Yoshiyasu Yamakawa
Title: Types of storms and other severe weather events cause both public health and economic problems for communities/municipalities. The data is from NOAA storm database. 
Synopsis: 
Date: 5/11/2016
output: html_document
---

## Question 1: Across the United States, which types of events (as indicated in the EVTYPE variable) are most harmful with respect to population health?

# Step 1: Download a file and load the data into storm_data  

```{r echo=TRUE, cache=TRUE}
setwd("D:/_work/_Training/Data_Science/All_Course_Content/Lesson5 Reproducible Research/Projects/Assignment_2")
download.file("https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2FStormData.csv.bz2", "storm_data.csv.bz2")
storm_data <- read.csv("./storm_data.csv.bz2", header = TRUE, sep = ",", quote = "\"")
head(storm_data)
dim(storm_data)
```

# Step 2: Data Processing - Aggregate sum of FATALITIES and INJURYtotal incidents by EVTYPE. Then take subset of Top20 of Fatality and Injury.  Then compare them with bar plot. 

```{r echo=TRUE}
# Calculate sum of fatalities by event type
fatality <- aggregate(storm_data$FATALITIES, list(type = storm_data$EVTYPE), sum, na.rm=TRUE)
names(fatality) <- c("type", "f_total")
# Calculate sum of injuries by event type
injury <- aggregate(storm_data$INJURIES, list(type = storm_data$EVTYPE), sum, na.r, = TRUE)
names(injury) <- c("type", "i_total")
# Merge Fatalities and Injuries by event type
mrg_data <- merge(fatality, injury, by = "type")
# Sort by fatality and injury
mrg_data_sort <- mrg_data[order(-mrg_data$f_total, -mrg_data$i_total),]
# Subset of top 20
mrg_data_sort_20 <- mrg_data_sort[1:20,]
mrg_data_sort_20$type <- factor(mrg_data_sort_20$type, levels = mrg_data_sort_20$type)
#

```

# 3. Result: 

```{r echo=TRUE}
library(ggplot2)
png(filename = "Fatality.png", width = 600, height = 480, units = "px")
ggplot(mrg_data_sort_20, aes(x=mrg_data_sort_20$type, y=mrg_data_sort_20$f_total, fill=mrg_data_sort_20$type)) + 
        geom_bar(stat = "identity") +
        xlab("Weather Type") +
        ylab("Number of Fatalities") +
        ggtitle("Top 20 Type of weather causing fatality")
dev.off()
png(filename = "Injury.png", width = 600, height = 480, units = "px")
ggplot(mrg_data_sort_20, aes(x=mrg_data_sort_20$type, y=mrg_data_sort_20$i_total, fill=mrg_data_sort_20$type)) + 
        geom_bar(stat = "identity") +
        xlab("Weather Type") +
        ylab("Number of Injuries") +
        ggtitle("Top 20 Type of weather causing injury")
dev.off()
```

# 4.  Analysis:
```

```

## Question 2: Across the United States, which types of events have the greatest economic consequences?

# Step 1: Download a file and load the data into storm_data  
```{r}
I will be using the same data frame from Question #1
```

# Step 2: Data Processing: Aggregate sum of PROPDMG and CROPDMG by event type
First
CROPDMGEXP 

```{r echo=TRUE}

```